State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-05-27 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
paper edits, switching conv

Substituting equation~\ref{DefGamma} into equation~\ref{StartofReduction} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 

@@

&+&\xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.\\ 

@@

@@

	\mathbf x_{n}&=&\mathbf x_{n-1}+T_s \mathbf Q(\mathbf x_{n-1}) \boldsymbol{\theta}-\zeta T_s\mathbf x_{n-1}+\mathbf e_{n-1} \nonumber

@@

		\mathbf x_{n}-\mathbf x_{n-1}

@@

		\mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}

>>>>

Now defining
\begin{equation}\label{eq:DefGamma2}
	\boldsymbol{\Gamma} = \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)d\mathbf{r}}, 
and substituting equation~\ref{eq:DefGamma2} into equation~\ref{StartofReduction} and cross-multiplying by $\boldsymbol{\Gamma}^{-1}$ gives 

@@

&+&\xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.

@@

Equation~\ref{eq:ReducedForm} can be simplified by exploiting the symmetry (isotropy) of the connectivity kernel where
	\boldsymbol{\psi} (\mathbf{r}-\mathbf{r}') = \boldsymbol{\psi} (\mathbf{r}'-\mathbf{r}).
To make the simplification we first define
\begin{equation}\label{eq:DefPsi}
	\boldsymbol{\Psi}(\mathbf{r}') = T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi} (\mathbf{r}'-\mathbf{r})d\mathbf{r}},
which is constant and can be defined analytically. Now substituting~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives
	\mathbf{x}_{t+1} \nonumber = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.

@@

	\mathbf x_{T}&=&\mathbf x_{T-1}+T_s \mathbf Q(\mathbf x_{T-1}) \boldsymbol{\theta}-\zeta T_s\mathbf x_{T-1}+\mathbf e_{n-1} \nonumber

@@

		\mathbf x_{T}-\mathbf x_{T-1}

@@

		\mathbf Q(\mathbf x_{T-1})&-\mathbf x_{T-1}
